Appendix for 'Framing Effects in the Wild

### 2022-09-07 paper/appendix.Rmd
Add section on crowding out

>>>>

```
## Crowding out

```{r crowdout}

gles_long <- 
  fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
  select(lfdn, date_clean, wave, 
         `1661a_clean`:`1661g_clean`, `1600_clean`, `1681f_clean`,
         `1130_clean`, post, treat)

gles_long <- 
  gles_long %>% 
  mutate(
    other_print = 
      `1661b_clean` +
      `1661c_clean` +
      `1661d_clean` +
      `1661e_clean` +
      `1661f_clean` +
      `1661g_clean`,
    dv = `1130_clean`,
    tv_use = `1681f_clean`,
    in_use = `1600_clean`,
    treat = as.factor(treat),
    post = as.factor(post)
  ) %>% 
  mutate(other_print = 
           case_when(
             other_print == 0 ~ "0",
             other_print > 0  & 
               other_print <= 3 ~ "1-3",
             other_print > 3  & 
               other_print <= 9 ~ "4-9",
             other_print > 9  & 
               other_print <= 15 ~ "10-15",
             other_print > 15 ~ ">15"
           )
        ) %>% 
  filter(!wave %in% c("a1", "a2"))

ests <- 
  data.frame(
    CATE = NULL,
    CATE_lower = NULL,
    CATE_upper = NULL,
    value = NULL,
    moderator = NULL
  )

for (mod in c("tv_use", "in_use", "other_print")){

  values <- 
    gles_long %>%
    filter(!is.na(get(mod))) %>% 
    select(mod) %>% 
    unique() %>% 
    .[[1]]

  for (value in values){

    temp <- 
      gles_long %>% 
      filter(get(mod) == value)

    m <- 
      fixest::feglm(dv ~ post*treat | ID + Wave, 
                  data = 
                    temp %>% 
                    filter(!is.na(dv)) %>% 
                    mutate(
                      Wave = 
                        ifelse(
                          wave %in% sort(unique(.$wave))[c(1, 2)],
                          "reference",
                          wave
                        ),
                      ID = lfdn
                    ) %>% 
                    select(dv, post, treat, ID, Wave),
                  cluster = c("ID", "Wave"))

    ests <- 
      rbind(
        ests,
        data.frame(
          CATE = m$coefficients["postTRUE:treatTRUE"],
          CATE_lower = confint(m)["postTRUE:treatTRUE", "2.5 %"],
          CATE_upper = confint(m)["postTRUE:treatTRUE", "97.5 %"],
          value = value,
          moderator = mod
        )
      )

  }

}

ests <- 
  ests %>% 
  mutate(
    effect_label = 
      ifelse(
        value == "0",
        as.character(round(CATE, 3)),
        ""
      ),

  )

varnames <- 
  list(
    "in_use" = "Internet use", 
    "other_print" = "Days other print consumed", 
    "tv_use" = "TV use")

labeller <- function(variable,value){
  return(varnames[value])
}

ests %>%
  ggplot(aes(x = factor(value,
                        levels = as.character(c(0, 1, "1-3", 2, 3, 4, "4-9", 
                                              5, 6, 7, 8, 9, 10, "10-15",
                                              ">15"))), 
             y = CATE, ymin = CATE_lower, ymax = CATE_upper,
             col = value != "0")) +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = c(0.15, -0.15), lty = 3) +
  geom_hline(yintercept = c(0.6, -0.6), lty = 2) +
  geom_pointrange() +
  geom_text(aes(x = "0", 
                y = CATE, 
                label = effect_label,
                hjust = -.3)
            ) +
  facet_wrap(~moderator, scales = "free_x",
             labeller = labeller) +
  theme_minimal() +
  xlab("") +
  theme(legend.position = "None")
